Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Fix typo.

The Raft algorithm breaks the problem of consensus into three core
sub-problems: leader election, log replication, and safety
\cite[Section~3]{raft_thesis:ongaro14}. A full Raft system must also
address: cluster membership changes
\cite[Section~4]{raft_thesis:ongaro14}, log compaction
\cite[Section~5]{raft_thesis:ongaro14}, and client
interaction \cite[Section~6]{raft_thesis:ongaro14}. The Raft protocol
is based on the concept of a distributed transaction log. Entries in
the log represent a sequence of commands that will be applied to an
internal state machine. If all members of the Raft cluster have the
same log entries, then their state machine on each node will have
exactly the same state. Each node of a Raft cluster can be in one of
three states: follower, candidate, or leader. The responsibility of
the leader is to accept new transaction log entries and then
replicated these entries in the same order to all other members of the
cluster. The leader is the only member of the cluster that may make
changes to the transaction log. In order to maintain leadership, the
leader sends heartbeat RPCs to all the followers in the cluster.
Followers that do not receive a heartbeat RPC within a certain time
period become candidates and attempt to be elected by the other nodes
as the new leader of the cluster \cite[p.~12]{raft_thesis:ongaro14}.

>>>>

The Raft algorithm breaks the problem of consensus into three core
sub-problems: leader election, log replication, and safety
\cite[Section~3]{raft_thesis:ongaro14}. A full Raft system must also
address: cluster membership changes
\cite[Section~4]{raft_thesis:ongaro14}, log compaction
\cite[Section~5]{raft_thesis:ongaro14}, and client
interaction \cite[Section~6]{raft_thesis:ongaro14}. The Raft protocol
is based on the concept of a distributed transaction log. Entries in
the log represent a sequence of commands that will be applied to an
internal state machine. If all members of the Raft cluster have the
same log entries, then their state machine on each node will have
exactly the same state. Each node of a Raft cluster can be in one of
three states: follower, candidate, or leader. The responsibility of
the leader is to accept new transaction log entries and then
replicate these entries in the same order to all other members of the
cluster. The leader is the only member of the cluster that may make
changes to the transaction log. In order to maintain leadership, the
leader sends heartbeat RPCs to all the followers in the cluster.
Followers that do not receive a heartbeat RPC within a certain time
period become candidates and attempt to be elected by the other nodes
as the new leader of the cluster \cite[p.~12]{raft_thesis:ongaro14}.
